### 2019-06-10 NFES_Review/Chapters/_tbl_Collection.tex
min feature

\begin{table}[th]
\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
%\begin{center}
% total table width eq 0.91\textheight = 100%
\begin{tabular}{
>{\raggedright\arraybackslash}p{0.130\textheight}
>{\raggedright\arraybackslash}p{0.130\textheight}
>{\raggedright\arraybackslash}p{0.090\textheight}
>{\raggedright\arraybackslash}p{0.310\textheight}
>{\raggedright\arraybackslash}p{0.180\textheight}
>{\raggedright\arraybackslash}p{0.060\textheight} }  
\hline
Polymer & Solvent & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Reference \\
\hline
Poly(ethylene oxide) (PEO) &
Deionized water &
Low-Voltage and Low-Electrical Field NFES &
\begin{itemize}[leftmargin=*]
\item PEO Concentration: 1, 2, and 3 $w t \%$
\item Rise in solution conductivity with the increase in PEO concentration
\item Solution Stirring: 24 $h$ of free diffusion followed by 96 $h$ of stirring at 30 $r p m$
\item 3 $m L$ syringe
\item 27 gauge type 304 stainless steel needle
\item Solution deposition rate: lower than 1 $\mu L / h$
\item needle-to-collector distance: 1 $m m$
\end{itemize} &
\begin{itemize}[leftmargin=*]
\item Diameter: 50-425 $n m$
\end{itemize} &
\cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
\hline
\label{tbl:FloresCompare}
\end{tabular}
%\end{center}
\end{table}

\begin{table}[th]
\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
%\begin{center}
% total table width eq 0.91\textheight = 100%
\begin{tabular}{
>{\raggedright\arraybackslash}p{0.130\textheight}
>{\raggedright\arraybackslash}p{0.130\textheight}
>{\raggedright\arraybackslash}p{0.090\textheight}
>{\raggedright\arraybackslash}p{0.310\textheight}
>{\raggedright\arraybackslash}p{0.180\textheight}
>{\raggedright\arraybackslash}p{0.060\textheight} } 
\hline
Polymer & Solvent & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Reference \\
\hline
 &
 &
 &
\begin{itemize}[leftmargin=*]
\item NFES process initiated by an air interference with a glass microprobe tip (1 to 3 $\mu m$ tip diameter) to overcome the surface tension
\item Time to produce a stable continuous jet: 45 $min$
\item Polymer jet initiated at 400-600 $V$ and dispensed at 200-400 $V$
\item Collector linear speed: 10-40 $m m / s$
\item The voltage turned on when the solution formed a full-sized droplet of 500 $\mu m$ diameter at the needle tip.
\end{itemize} &
 &
\cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
\hline
Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with Poly(ethylene oxide) (PEO) &
acetonitrile / toluene mixture (65 / 35); acetic acid / toluene (17 / 83); pure toluene &
 &
\begin{itemize}[leftmargin=*]
\item Concentrations:
    \begin{itemize}[leftmargin=*]
    \item MEH-PPV solution: 10 $m g$ of MEH-PPV in 2 $m L$ of toluene
    \item 500 $\mu L$ of MEH-PPV solution with 250 $m g$ of PEO in 3.5 $m L$ of acetonitrile / toluene (65 / 35)
    \item 500 $\mu L$ of MEH-PPV solution with 250 $m g$ of PEO in 3 $m L$ of acetic acid / toluene (17 / 83)
    \end{itemize}
\end{itemize} &
 &
\cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
\hline
\label{tbl:FloresCompare}
\end{tabular}
%\end{center}
\end{table}

\begin{table}[th]
\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
%\begin{center}
% total table width eq 0.91\textheight = 100%
\begin{tabular}{
>{\raggedright\arraybackslash}p{0.130\textheight}
>{\raggedright\arraybackslash}p{0.130\textheight}
>{\raggedright\arraybackslash}p{0.090\textheight}
>{\raggedright\arraybackslash}p{0.310\textheight}
>{\raggedright\arraybackslash}p{0.180\textheight}
>{\raggedright\arraybackslash}p{0.060\textheight} } 
\hline
 &
 &
 &
\begin{itemize}[leftmargin=*]
\item[]
    \begin{itemize}[leftmargin=*]
    \item The resulting MEH-PPV/PEO concentration is 1:100
    \end{itemize}
\item Solution Stirring:
    \begin{itemize}[leftmargin=*]
    \item MEH-PPV solution stirred for 4 $h$
    \item PEO solution stirred for 8 $h$
    \item MEH-PPV/PEO solution stirred and ultrasonically agitated
    \end{itemize}
\item Collector substrate: SiO2/Si (oxide thickness = 800 $n m$)
\item needle-to-collector distance: 500 $\mu m$
\item $\mu m$-diameter tip Tungsten spinneret in a 26 gauge needle
\item Solution deposition rate: 50 $\mu L / h$
\item Electrostatic voltage: around 1.3 $k V$
\item x-y stage velocity: 50 $c m / s$
\end{itemize} &
\begin{itemize}
\item distance between adjacent fibers: around 100 $\mu m$
\item Fiber diameter: around 100 $n m$
\end{itemize} &
\cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
\hline
\label{tbl:FloresCompare}
\end{tabular}
%\end{center}
\end{table}

@@

\addtolength{\oddsidemargin}{0.0in}
\addtolength{\evensidemargin}{0.0in}
\addtolength{\topmargin}{0.0in}

>>>>

\begin{table}[th]
\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
%\begin{center}
% total table width eq 0.91\textheight = 100%
\begin{tabular}{
>{\raggedright\arraybackslash}p{0.130\textheight}
>{\raggedright\arraybackslash}p{0.130\textheight}
>{\raggedright\arraybackslash}p{0.090\textheight}
>{\raggedright\arraybackslash}p{0.310\textheight}
>{\raggedright\arraybackslash}p{0.180\textheight}
>{\raggedright\arraybackslash}p{0.060\textheight} }  
\hline
Polymer & Solvent & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Reference \\
\hline
Poly(ethylene oxide) (PEO) &
Deionized water &
Mechano electrospinning &
\begin{itemize}[leftmargin=*]
\item PEO Concentration: 1, 2, and 3 $w t \%$
\item Rise in solution conductivity with the increase in PEO concentration
\item Solution Stirring: 24 $h$ of free diffusion followed by 96 $h$ of stirring at 30 $r p m$
\item 3 $m L$ syringe
\item 27 gauge type 304 stainless steel needle
\item Solution deposition rate: lower than 1 $\mu L / h$
\item needle-to-collector distance: 1 $m m$
\item Collector substrate: Pyrolyzed SU-8 carbon and Si
\end{itemize} &
\begin{itemize}[leftmargin=*]
\item Diameter: 50-425 $n m$
\end{itemize} &
\cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
\hline
\label{tbl:FloresCompare}
\end{tabular}
%\end{center}
\end{table}

\begin{table}[th]
\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
%\begin{center}
% total table width eq 0.91\textheight = 100%
\begin{tabular}{
>{\raggedright\arraybackslash}p{0.130\textheight}
>{\raggedright\arraybackslash}p{0.130\textheight}
>{\raggedright\arraybackslash}p{0.090\textheight}
>{\raggedright\arraybackslash}p{0.310\textheight}
>{\raggedright\arraybackslash}p{0.180\textheight}
>{\raggedright\arraybackslash}p{0.060\textheight} } 
\hline
Polymer & Solvent & NFES Variant & Polymer Solution and Process Properties & Fiber Characterization & Reference \\
\hline
 &
 &
 &
\begin{itemize}[leftmargin=*]
\item NFES process initiated by an air interference with a glass microprobe tip (1 to 3 $\mu m$ tip diameter) to overcome the surface tension
\item Time to produce a stable continuous jet: 45 $min$
\item Polymer jet initiated at 400-600 $V$ and dispensed at 200-400 $V$
\item Collector linear speed: 10-40 $m m / s$
\item The voltage turned on when the solution formed a full-sized droplet of 500 $\mu m$ diameter at the needle tip.
\end{itemize} &
 &
\cite{Bisht2011}   \\ %Controlled Continuous Patterning of Polymeric Nanofibers on Three-Dimensional Substrates Using Low-Voltage Near-Field Electrospinning
\hline
Poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with Poly(ethylene oxide) (PEO) &
acetonitrile / toluene mixture (65 / 35); acetic acid / toluene (17 / 83); pure toluene &
Mechano electrospinning &
\begin{itemize}[leftmargin=*]
\item Concentrations:
    \begin{itemize}[leftmargin=*]
    \item MEH-PPV solution: 10 $m g$ of MEH-PPV in 2 $m L$ of toluene
    \item 500 $\mu L$ of MEH-PPV solution with 250 $m g$ of PEO in 3.5 $m L$ of acetonitrile / toluene (65 / 35)
    \item 500 $\mu L$ of MEH-PPV solution with 250 $m g$ of PEO in 3 $m L$ of acetic acid / toluene (17 / 83)
    \end{itemize}
\end{itemize} &
\begin{itemize}
\item Distance between adjacent fibers: around 100 $\mu m$
\item Fiber diameter: around 100 $n m$
\end{itemize} &
\cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
\hline
\label{tbl:FloresCompare}
\end{tabular}
%\end{center}
\end{table}

\begin{table}[th]
\caption{Electrospun Polymer Solutions - Solution and Process Parameters}
%\begin{center}
% total table width eq 0.91\textheight = 100%
\begin{tabular}{
>{\raggedright\arraybackslash}p{0.130\textheight}
>{\raggedright\arraybackslash}p{0.130\textheight}
>{\raggedright\arraybackslash}p{0.090\textheight}
>{\raggedright\arraybackslash}p{0.310\textheight}
>{\raggedright\arraybackslash}p{0.180\textheight}
>{\raggedright\arraybackslash}p{0.060\textheight} } 
\hline
 &
 &
 &
\begin{itemize}[leftmargin=*]
\item[]
    \begin{itemize}[leftmargin=*]
    \item The resulting MEH-PPV/PEO concentration is 1:100
    \end{itemize}
\item Solution Stirring:
    \begin{itemize}[leftmargin=*]
    \item MEH-PPV solution stirred for 4 $h$
    \item PEO solution stirred for 8 $h$
    \item MEH-PPV/PEO solution stirred and ultrasonically agitated
    \end{itemize}
\item Collector substrate: SiO2/Si (oxide thickness = 800 $n m$)
\item needle-to-collector distance: 500 $\mu m$
\item $\mu m$-diameter tip Tungsten spinneret in a 26 gauge needle
\item Solution deposition rate: 50 $\mu L / h$
\item Electrostatic voltage: around 1.3 $k V$
\item x-y stage velocity: 50 $c m / s$
\end{itemize} &
 &
\cite{Camillo2013} \\ %Near-field electrospinning of conjugated polymer light-emitting nanofibers
\hline
\label{tbl:FloresCompare}
\end{tabular}
%\end{center}
\end{table}

@@

%\addtolength{\oddsidemargin}{0.0in}
%\addtolength{\evensidemargin}{0.0in}
\addtolength{\topmargin}{0.0in}
